---
title: "Using the `powers` package"
author: "Alex Cheng"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the `powers` package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

__Note__: This package isn't actually meant to be "serious". Vincenzo Coia made it just for teaching purposes, and I have edited it to include a Box Cox Transformation function as part of STAT547M Assignment 7.

Want to compute powers without having to use `^` or `**`? Give `sqrt` some friends by loading the `powers` package! 

```{r}
library(powers)
```

Want squares, cubes, or reciprocals? Easy.

```{r}
square(1:10)
cube(1:10)
reciprocal(1:10)
```

`apply`-family friendly, too!

```{r}
my_list <- list(1:10, 0.5, -0.7)
## So base-R-boring!
lapply(my_list, function(x) x^2)
## Use powers instead!
lapply(my_list, square)
```

It even comes with the ability to display its output in plot form!

```{r}
reciprocal(1:10, plot_it=TRUE)
```

Is your data suffering from non-normality or heteroscedasticity? A Box Cox transformation may help! Just enter your data into the `bc_transform()` function.

```{r}
# Non-normal data!
hist(skewvec)
bc_transform(skewvec) # Default lambda value is 0

# Slightly better looking data even with a default lambda value!
hist(bc_transform(skewvec))

# Much better looking data with a lambda of 0.25!
hist(bc_transform(skewvec, 0.25))

# We can see that the variance in the data is now much smaller!
sd(skewvec)
sd(bc_transform(skewvec))
```

